### 2018-09-10 manuscript.tex
Update manuscript.tex

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules (checked in 09/17).

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (need more work). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory. \cf{need comments!!!}

(see \cite{IloDarf18, PashPonn16} for measurements of the thoery of planned behaviors on fgc)

(CF: Can domestic violence index (gender power) be a proxy to perceived controlled behavior for daugther's FGC future?)

The main response variables were woman's intention of cutting their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model .  The main predictors were attitudes of FGC benefits and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.

The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural).  The followings were treated as random variables:  cluster ID (villages), countries and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).  Further, media effect was also counted in the random effect (slope?) because we presumed that each country carried various media content from each other.

In order to address the significance of community impact on the practice, FGC prevalence was calculated on a cluster level \CF{right?} and applied in the models as part of the (wording...). Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).  We also tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).

 \_\_{[}CF:Do we splne wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}

%“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. “ \cite{Hayf05}

\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  Same reason as for clusterID{]}

@@

-----stop reading -----
% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

>>>>

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not analyze the newest dataset due to the lack of FGC benefits modules before this study finished for publication (checked in 09/17).

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} and applied in fgc studies (e.g., \{IloDarf18, PashPonn16}(more cites?). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  Here, we refer the attitudes to women's attitudes of FGC benefits (see the list of FGC benefits at table-- in Appendix); perceived behavioral control to perception of gender awareness (i.e., women's attitudes towards domestic violence (see the list of attitudes towards domestic violence against women at table xx) and to their social resources (education, and job?) (feminism and modernization?); and the perceived social pressures (subjective norms) as the community level of attitudes of FGC benefits and FGC prevalence (to reflect the convention norms of FGC under the convention theory). \cf{need comments!!!}

The main response variables in this study were woman's intention to cut their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model.  The main predictors were attitudes of FGC benefits and woman's FGC status.  In order to test other theories mentioned above, we also included woman's gender awareness and other socio demogramic variables (see below).

The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural).  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).  (We did not treat media effect  in the random effect (slope?) because we presumed that each country carried media content different from each other.  Why not?)

In order to address the significance of community impact on the practice were education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level (on a cluster leve, not national, right?), which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}). Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).

\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  Same reason as for clusterID{]} %“explicitly including ethnicity is a means of assessing another dimension of the collective aspect of circumcision behavior. “ \cite{Hayf05}

@@

-----stop reading -----

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))
